\vspace{-0.5cm} XSGRB - The X-shooter GRB afterglow sample

### 2018-02-05 document/tables/redshift_comparison.tex
Many comments and notes on individual bursts
Final draft sent around

\begin{table}[H]
	\centering
	\begin{tabular}{ccccc}
		\hline
		\hline\noalign{\smallskip}
		{Sample} & {N$_{\mathrm{bursts}}$} & {z$_{\mathrm{completeness}}$} &  {z$_{\mathrm{mean}}$} &  {$z_{\mathrm{med}}$} \\
		\hline\noalign{\smallskip}
		{\smallskip}
		XS-GRB & 125 & 84 \% & 1.86 & $1.46_{-0.86}^{+1.77}$ \\
		{\smallskip}
		SHOALS  & 119 &  99 \% &  2.18  & $2.06_{-1.20}^{+1.27}$ \\
		{\smallskip}
		BAT6 & 58 & 95 \% &  1.90 &  $1.71_{-1.04}^{+1.31}$ \\
		{\smallskip}
		TOUGH & 69 &  77 \% & 2.20 & $2.11_{-1.36}^{+1.42}$ \\
		{\smallskip}
		Fynbo09 & 146 &  49 \% &  2.2 & $2.1_{-1.23}^{+1.28}$ \\
		\hline\noalign{\smallskip}

>>>>

\begin{table}[H]
	\centering
	\begin{tabular}{ccccc}
		\hline
		\hline\noalign{\smallskip}
		{Sample} & {N$_{\mathrm{bursts}}$} & {$z_{\mathrm{completeness}}$} &  {$z_{\mathrm{mean}}$} &  {$z_{\mathrm{med}}$} \\
		\hline\noalign{\smallskip}
		{\smallskip}
		XS-GRB & 129 & 88 \% & 1.89 & $1.52_{-0.91}^{+1.83}$ \\
		{\smallskip}
		SHOALS  & 119 &  99 \% &  2.18  & $2.06_{-1.20}^{+1.27}$ \\
		{\smallskip}
		BAT6 & 58 & 95 \% &  1.90 &  $1.71_{-1.04}^{+1.31}$ \\
		{\smallskip}
		TOUGH & 69 &  77 \% & 2.20 & $2.11_{-1.36}^{+1.42}$ \\
		{\smallskip}
		Fynbo09 & 146 &  49 \% &  2.2 & $2.1_{-1.23}^{+1.28}$ \\
		\hline\noalign{\smallskip}
